Supplementary Material for 'New insights into the Weddell Sea ecosystem applying

### 2023-10-24 Manuscript/SupMaterial.Rmd
Update Appendices Add taxonomic classification
Exponents variability

@@

$$
\begin{aligned}
IS = \alpha X_R \frac{m_R}{m_C}\\
\end{aligned}
$$
where $\alpha$ is the search rate, $X_R$ is the resource density, and $m_R$ and $m_C$ are the body mass for the resource and the consumer, respectively [@Pawar2012].

>>>>

### Weighted properties: Interaction Strength

@@

$$
\begin{aligned}
IS = \alpha X_R \frac{m_R}{m_C}\\
\end{aligned}
$$
where $\alpha$ is the search rate, $X_R$ is the resource density, and $m_R$ and $m_C$ are the body mass for the resource and the consumer, respectively [@Pawar2012]. We assume the case were resources are scarce because this resembles field conditions (figure 3 e & f and equation 3 from @Pawar2012).
Then the search rate for 2D interactions (see main text) is calculated as:

$$\alpha = \alpha_{2D} m_C^{0.68 \pm 0.12}$$
For 3D interactions it is calculated as:

$$\alpha = \alpha_{3D} m_C^{1.05 \pm 0.08}$$

where $\alpha_{2D}=10^{-3.08}$ and $\alpha_{3D}=10^{-1.77}$ are the intercepts for each interaction dimensionality.

As the resource density $X_R$ is not known we estimated it according to the equation S18 and supplementary figures 2i & j (individuals/m2 - m3)

$$X_R = X_0 m_R^{-p_x}$$

were $p_x$ is -0.79±0.08 for 2D and -0.86±0.07 for 3D.

### Unweighted properties
